A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-09 paper.tex
related work

Of course, a space-efficient cast representation must be proved
correct. That is, a language implementation that uses space-efficient
casts should give the same output as the language semantics. Our
generic CEK machine comes with generic theorems mechanized in
the Agda proof assistant~\citep{norell2008dependently}
(Section~\ref{sec:framework}) that researchers can use to prove a cast
representation correct.  We believe this framework can reduce the
burden of proving correctness theorems and help people focus on the
cast representations. As a demonstration, we apply the framework to
Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
and Lazy UD threesomes~\citep{Siek:2010:TWB:1706299.1706342}. We
believe the framework is also applicable to other cast
representations. The framework and demonstrations are available at the
following URL:
\[\text{\urlFrameworkAndIllustration}\]
\todo[inline]{KC: is this the right place to mention that in Agda
code we use de Bruijn indexes?}

@@

\todo[inline]{KC: This paragraph suggests that
\cite{siek2009exploring} gives the definitional semantics.
\cite{siek2009exploring}'s is coercion-based.
It makes more sense to me to use a type-based semantics as the definition.
Actually in my mind \cite{siek2012interpretations} is definitional.}

@@

\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related
  work section from the eyes of the reviewer.}
\todo[inline]{KC: I might have some misconcept about the related work section.
You might have felt this, haha. Now I think this section is targeting the
following scenarios: 
- ``I think someone has solved this problem ...''
- ``This work looks similar to paper X, what is the difference?''
- ``Is this work inspired by paper X?''
Is my understanding correct?}
\todo[inline]{JS: yes, and make sure to
  give very explicit answers to these questions. It should feel to you
  like you're hitting the reader over the head with the most obvious
  things (to you). The above paragraph is currently insufficient
  because it doesn't emphasize what scientific constributions are new
  to our paper compared to those prior papers on coercions in normal
  form.}
\todo[inline]{KC: I rewrote this section. Please check again.}

\subsection{Dynamics semantics parameterized over cast representations}
\citet{siek2020mechanized} defines two dynamic semantics for 
cast calculi parameterized over cast representations. The first
semantics, namely CC, is \textit{not} space-efficient and
parameterized over $\mathrm{CastStruct}$. The author instantiates
CC to obtain the blame calculus ($\lambda B$) in 
\cite{Siek:2010:TWB:1706299.1706342}. 
The resulting semantics is analogous to our \LUDMachine.
The other semantics, namely SC, is designed to be space-efficient
and parameterized over $\mathrm{EfficientCastStruct}$. SC is analogous
to our \SMachine{C}. CC and SC give their users more control
over the structure of values. Our \CMachine{B} machine
insists that the cast on the top of a value must be a cast between
compound types (specifically, functions and pairs).
In contrast, users of their interfaces define
a predicate on casts called $\mathrm{Inert}$ and any inert cast can
be a part of a value. Their system doesn't include theorems relating
space-inefficient cast calculi and space-efficient ones, which
is one of the major goals of our framework.

@@

\todo[inline]{JS: The above is too short of a description of that related
work.}
\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
of dynamic semantics by applying the correspondence described
through the paper starting with a different set of coercion artefacts.''.
However they didn't give a generalization and it is unclear to me over what
their system is parameterized (cast representations? apply-coercion and seq?.}

@@

\citet{Garcia:2013:CTB:2500365.2500603}
introduces several other flavors of threesomes, including a Lazy D
one. Their threesomes are derived from the corresponding styles of
coercions in \citet{herman2010space}, using correctness-preserving
transformation.

\cite{Siek:2015:BCT:2737924.2737968} proves the correctness
of \LUD\ coercions in normal form. Their approach is similar to
that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
three calculi (i.e. $\lambda B$ and $\lambda C$ and $\lambda S$). 
$\lambda B$ is the blame calculus. 
$\lambda C$ uses coercions but doesn't normalize coercions
so is not space-efficient. $\lambda S$ uses coercions in normal form
and is space-efficient. To establish the correctness of
their cast representation,
they prove a bisimulation relating $\lambda B$ to $\lambda C$
and a bisimulation relating $\lambda C$ to $\lambda S$.
Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
and \cite{Siek:2015:BCT:2737924.2737968}, 
we also use the bisimulation technique.

>>>>

Of course, a space-efficient cast representation must be proved
correct. That is, a language implementation that uses space-efficient
casts should give the same output as the language semantics. Our
generic CEK machine comes with generic theorems mechanized in
the Agda proof assistant~\citep{norell2008dependently}
(Section~\ref{sec:framework}) that researchers can use to prove a cast
representation correct.  We believe this framework can reduce the
burden of proving correctness theorems and help people focus on the
cast representations. As a demonstration, we apply the framework to
Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
and Lazy UD threesomes~\citep{Siek:2010:TWB:1706299.1706342}. We
believe the framework is also applicable to other cast
representations. The framework and demonstrations are available at the
following URL:
\[\text{\urlFrameworkAndIllustration}\]
\todo[inline]{KC: is this the right place to mention that in Agda
code we use de Bruijn indexes?}
\todo[inline]{JS: no, that's too deep into the details for the introduction
   of a paper that is not about variable representations.}

@@

\todo[inline]{KC: This paragraph suggests that
\cite{siek2009exploring} gives the definitional semantics.
\cite{siek2009exploring}'s is coercion-based.
It makes more sense to me to use a type-based semantics as the definition.
Actually in my mind \cite{siek2012interpretations} is definitional.}
\todo[inline]{JS: While I see what you're saying, its important
  to give precendence to the definition that is earlier in time.}

@@

\todo[inline]{JS: add a sentence that summarizes this section,
  mentioning the topics of the two subsections.}

\subsection{Dynamics semantics parameterized over cast representations}

\citet{siek2020mechanized} defines two reduction semantics for cast
calculi parameterized over cast representations. The first semantics,
namely CC, is not space-efficient and is parameterized over
$\mathrm{CastStruct}$.  The reduction semantics for CC is analogous to
our \LUDMachine.  The second semantics, namely SC, is designed to be
space-efficient and parameterized over
$\mathrm{EfficientCastStruct}$. SC is analogous to our \SMachine{C}.
\citet{siek2020mechanized} does not prove the correctness of SC with
respect to CC, whereas the main goal of the present paper is proving
the correctness of \SMachine{C} with respect to \LUDMachine.

%% The following details are less important. -Jeremy
%% CC and SC give their users more control over the structure of
%% values. Our \CMachine{B} machine insists that the cast on the top of a
%% value must be a cast between compound types (specifically, functions
%% and pairs).  In contrast, users of their interfaces define a predicate
%% on casts called $\mathrm{Inert}$ and any inert cast can be a part of a
%% value.

@@

\todo[inline]{JS: The above is too short of a description of that related
work.}
\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
of dynamic semantics by applying the correspondence described
through the paper starting with a different set of coercion artefacts.''.
However they didn't give a generalization and it is unclear to me over what
their system is parameterized (cast representations? apply-coercion and seq?.}
\todo[inline]{JS: your comment above says what you should say
  (except the part about your confusion). Say it in a matter-of-fact
way, and not a derogitory way.}

@@

\citet{Garcia:2013:CTB:2500365.2500603}
introduces several other flavors of threesomes, including a Lazy D
one. Their threesomes are derived from the corresponding styles of
coercions in \citet{herman2010space}, using a correctness-preserving
transformation.

\cite{Siek:2015:BCT:2737924.2737968} proves the correctness
of \LUD\ coercions in normal form. Their approach is similar to
that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
three calculi (i.e. $\lambda B$ and $\lambda C$ and $\lambda S$). 
$\lambda B$ is the blame calculus. 
$\lambda C$ uses coercions but doesn't normalize coercions
so is not space-efficient. $\lambda S$ uses coercions in normal form
and is space-efficient. To establish the correctness of
their cast representation,
they prove a bisimulation relating $\lambda B$ to $\lambda C$
and a bisimulation relating $\lambda C$ to $\lambda S$.
Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
and \cite{Siek:2015:BCT:2737924.2737968}, 
we also use the bisimulation technique.
\todo[inline]{JS: there is a least one interesting difference regarding
  the bisimulation: your lemma 3 has an ``upto reduction'' flavor to it
  which makes your $\approx$ relation simpler. }
